%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\usepackage{enumitem}
\setlist{leftmargin=0em}
\renewcommand{\labelitemi}{$\cdot$}

%%MINE THAT I ADDED

\usepackage{lipsum}
\usepackage{datetime}
\usepackage{hyperref}
\usepackage{ragged2e}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

%---------------------------

\name{Katherine A. Keith} % Your name
\address{
%(406)~$\cdot$~539~$\cdot$~3888 \\ 
kkeith@cs.umass.edu} % Your phone number and email

\begin{document}

%%----------------------------------------------------------------------------------------
%%	RESEARCH INTERESTS
%%----------------------------------------------------------------------------------------
%
%\begin{rSection}{Research Interests}
%Natural language processing, machine learning, computational social science 
%\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Massachusetts Amherst} \hfill {2016--Present} \\ 
M.S.~/~Ph.D. in Computer Science (in progress) \hfill {\em Amherst, MA} \\

{\bf Lewis \& Clark College} \hfill {2011--2015} \\ 
B.A. in Mathematics, departmental honors, summa cum laude \hfill {\em Portland, OR}
\end{rSection}

%----------------------------------------------------------------------------------------
% RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{Graduate Research Assistant}{September 2016--Present}{University of Massachusetts, Amherst}{Amherst, MA}
\item Advisor: Dr. Brendan O'Connor 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   SELECTED PUBLICATIONS 
%----------------------------------------------------------------------------------------
%
\begin{rSection}{Peer-Reviewed Publications}
Uncertainty-aware generative models for inferring document class prevalence.
\textbf{Katherine A. Keith} and Brendan O'Connor. 
In \emph{Proceedings of Empirical Methods in Natural Language Processing (EMNLP)}. 2018. 

Monte Carlo Syntax Marginals for Exploring and Using Dependency Parses.
\textbf{Katherine A. Keith}, Su Lin Blodgett, and Brendan O'Connor.
In \emph{Proceedings of North American Chapter of the Association for Computational Linguistics} (NAACL). 2018.

Identifying civilians killed by police with distantly supervised entity-event extraction. 
\textbf{Katherine A. Keith}, Abram Handler, Michael Pinkham, Cara Magliozzi, Joshua McDuffie, and Brendan O'Connor. In \emph{Proceedings of Empirical Methods in Natural Language Processing (EMNLP)}. 2017. 

\end{rSection}

%----------------------------------------------------------------------------------------
%	INDUSTRY EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Industry Experience}

\begin{rSubsection}{Research Intern}{May--August 2018}{CTO Data Science Team, Bloomberg L.P.}{New York, New York}
\item Mentor: Amanda Stent
\item Correlated stock market signals with text of earnings call transcripts 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}

\begin{rSubsection}{Graduate Teaching Assistant \\ CS685: Advanced Natural Language Processing}{Spring 2018}{University of Massachusetts Amherst}{}
\item Assisted students with homework and conceptual questions during weekly office hours
\item Graded literature review assignment and in-class presentations 
\item Helped to design homeworks
\end{rSubsection}

\begin{rSubsection}{Fulbright English Teaching Assistant}{August 2015--June 2016}{U.S. Department of State}{Kinmen, Taiwan}
\item Taught first through sixth grade ESL courses in a public elementary school
\item Facilitated multi-cultural dialogue and programming
\end{rSubsection}

\end{rSection}

%\blfootnote{Updated: \today}

%\bigskip

\end{document}
